Deciding Bitvector Termination with Program Synthesis

### 2014-07-02 papers/termination/paper.tex
Limitations

{\bf Limitations.}
For ease of exposition, this language ignores features
such as dynamic memory allocation and function calls. 
\begin{itemize}
\item No procedures (this could be handled by computing function summaries).
\item Heap (Thor).
\item Nested loops.
\end{itemize}

>>>>

{\bf Limitations.}
Our algorithm decides termination of transition systems with finite state spaces.
The (non-)termination proofs take the form of ranking functions and program invariants
that are expressed in a quantifier free language.  This formalism is powerful
enough to handle a large fragment of C, but is not rich enough to analyse
code using any of the following features:

\begin{itemize}
\item Recursion (could probably do this).
\item Heap (Thor).
\item Arrays.
\end{itemize}
